---
title: "AFUNDAR_FA1"
author: "Audrie Lex L. Afundar"
date: "2025-01-30"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, include=FALSE}
library(ggplot2)
dataset<-read.csv("C:/Users/Audrie Lex Afundar/Downloads/cytof_one_experiment.csv")

```
## Number 1

Choose one of the columns of the dataset and make at least two plots showing its distribution (choose from ECDF, quantile, histogram, density estimate). What does the plot tell you about the distribution of the values in that column?

## ECDF

```{r}
column_data<-"KIR3DL1"
ggplot(dataset, aes(x=.data[[column_data]]))+stat_ecdf()+labs(x = column_data, y = "ECDF", title = paste("ECDF of", column_data))

```
In the ECDF plot, the y level indicates the cumulutive fraction of distributions while the x axis shows the expression level of KIR3DL1. In the context of cytof, the graph indicates a spike/rise near 0 suggesting a low expression level of KIR3DL1.


## Histogram

```{r}
ggplot(dataset, aes(x=.data[[column_data]]))+geom_histogram(binwidth=0.1)+
  labs(title = paste("Histogram of", column_data), x = column_data, y = "Frequency")

```
The histogram having a right skewed distribution strongly suggests a low expression level of KIR3DL1 on the experimented cells. Moreover, the tail part of the graphs shows a moderately high expression level of KIR3DL1. Paired with the ECDF (Showing that more than 50% is in the lower levels), it paints a much clearer that most cells have a low expression level while there are sub groups with moderate-high levels of KIR3DL1.

## Number 2
Choose any two of the columns of the dataset and make a Q-Q plot comparing the distributions. What does the Q-Q plot tell you about similarities or differences between the distributions of the values in the two columns?

## Q-Q plot
```{r}
column_data1<-"NKp44"
qq.df=as.data.frame(qqplot(dataset[[column_data]],dataset[[column_data1]]),plot.it=FALSE)
ggplot(qq.df,aes(x=x,y=y))+geom_point()+xlab("KIR3DL1")+ylab("NKp44")+geom_abline()+geom_point(alpha = 0.6, size = 2)

```

The Q-Q plot is comparing the distribution of NKp44 and KIR3DL1 expression levels. The plot clearly shows a non perfect linear relationship, meaning a strong deviation on the expression levels. The curves on the plot suggests higher low or no expression levels on both axis.